Rice yield improvements through plant breeding are offset by inherent yield declines over time

### 2018-02-25 output/breed_paper_revised.Rnw
Added comments, formatting.

\begin{figure}[H]
<<echo = FALSE, fig = TRUE, width = 7, height = 6>>=
library(ggplot2)
library(ggthemes)
ggplot(mod_data, aes(x = year, y = yield_kg/1000)) +
    geom_point(size = 0.5, alpha = 0.5) +
    geom_smooth(method = "lm", color = "black") +
    theme_few() +
    xlab("Year") +
    ylab(expression("Grain yield ( Mg ha"^-1~")")) + 
    facet_wrap(~id, ncol = 4)

>>>>

\begin{figure}[H]
<<echo = FALSE, fig = TRUE, width = 7, height = 6>>=
library(ggplot2)
library(ggthemes)
ggplot(mod_data, aes(x = year, y = yield_kg/1000)) +
    geom_point(size = 0.5, alpha = 0.5) +
    geom_smooth(method = "lm", color = "black") +
    theme_few() +
    xlab("Year") +
i    ylab(expression("Grain yield ( Mg ha"^-1~")")) + 
    facet_wrap(~id, ncol = 4)
